---
title: "dbtstmetaanalysis12mo"
author: "Jonathan"
date: "January 15, 2018"
output: pdf_document
---

# Load Packages
```{r}
install.packages("metafor")
library("metafor")

install.packages("esc")
library("esc")

install.packages("effsize")
library("effsize")

```


# Calculate Effect Sizes for Depression 
```{r}
# Safer et al. (2010) - beck depression inventory
e1 <- esc_mean_sd(grp1m = 10.36, grp1sd = 9.97, grp1n = 50, grp2m = 10.04, grp2sd = 7.84,
                  grp2n = 51, es.type = "logit", study = "safer et al")

# Safer et al. (2010) - ees depression 
e2 <- esc_mean_sd(grp1m = 2.12, grp1sd = 0.92, grp1n = 50, grp2m = 2.18, grp2sd = 0.89,
                  grp2n = 51, es.type = "logit", study = "safer et al") 

# Safer & Joyce (2011) - beck depression inventory
e3 <- esc_mean_sd(grp1m = 8, grp1sd = 8.6, grp1n = 41, grp2m = 13.1, grp2sd = 9.3,
                  grp2n = 60, es.type = "logit", study = "safer and joyce") 


depression12mo <- combine_esc(e1, e2, e3)

metafor::rma(yi = es, sei = se, method = "REML", data = depression12mo)

```

# Calculate Effect Sizes for Eating Behaviors 
```{r}
# Safer et al. (2010) - beck depression inventory
e1 <- esc_mean_sd(grp1m = 10.36, grp1sd = 9.97, grp1n = 50, grp2m = 10.04, grp2sd = 7.84,
                  grp2n = 51, es.type = "logit", study = "safer et al")

# Safer et al. (2010) - ees depression 
e2 <- esc_mean_sd(grp1m = 2.12, grp1sd = 0.92, grp1n = 50, grp2m = 2.18, grp2sd = 0.89,
                  grp2n = 51, es.type = "logit", study = "safer et al") 

# Safer & Joyce (2011) - beck depression inventory
e3 <- esc_mean_sd(grp1m = 8, grp1sd = 8.6, grp1n = 41, grp2m = 13.1, grp2sd = 9.3,
                  grp2n = 60, es.type = "logit", study = "safer and joyce") 


depression12mo <- combine_esc(e1, e2, e3)

metafor::rma(yi = es, sei = se, method = "REML", data = depression12mo)







# 