---
title: "dbtstmetaanalysis"
author: "Jonathan"
date: "January 15, 2018"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

# Load Packages
```{r}
#install.packages("metafor")
library("metafor")

#install.packages("esc")
library("esc")

#install.packages("effsize")
library("effsize")

#install.packages("compute.es")
library("compute.es")

#install.packages("ggplot2")
library("ggplot2")

```

##### Two group Pre and Post #################


# Effect Size of Anxiety 
```{r}

# Soler et al. (2009): Hamilton Rating Scale for Anxiety
anxiety1 <- esc_mean_sd(grp1m = 13, grp1sd = 5.46, grp1n = 42, grp2m = 16.56, grp2sd = 5,
                  grp2n = 37, es.type = "d", study = "Soler et al 2009")

# Safer et al. (2010): Emotional Eating Scale-Anxiety
anxiety2 <- esc_mean_sd(grp1m = 1.51, grp1sd = 0.87, grp1n = 43, grp2m = 1.81, grp2sd = 0.89,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Hirvikoski et al. (2011): Beck Anxiety Inventory
anxiety3 <- esc_mean_sd(grp1m = 15.08, grp1sd = 11.06, grp1n = 26, grp2m = 13.83, grp2sd = 10.14,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")



anxietyez <- combine_esc(anxiety1, anxiety2, anxiety3)

metafor::rma(yi = es, sei = se, method = "REML", data = anxietyez)

#  d =   -0.3231 (small) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8

```


# Effect size of Depression
```{r}

# Soler et al. (2009):  Hamilton Rating Scale for Depression 
# Assumed N1, N2
depression1 <- esc_mean_sd(grp1m = 11.11, grp1sd = 3.99, grp1n = 23, grp2m = 16, grp2sd = 5.78,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Hirvikoski et al. (2011): Beck Depression Inventory 
depression2 <- esc_mean_sd(grp1m = 16.60, grp1sd = 10.19, grp1n = 26, grp2m = 14.36, grp2sd = 11.41,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")

# Safer et al. (2010): Emotional Eating Scale-Depression
depression3 <- esc_mean_sd(grp1m = 2.06, grp1sd = 0.99, grp1n = 43, grp2m = 1.81, grp2sd = 0.89,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Beck Depression Inventory
depression4 <- esc_mean_sd(grp1m = 9.10, grp1sd = 9.21, grp1n = 43, grp2m = 10.84, grp2sd = 6.86,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2001): Beck Depression Inventory
depression5 <- esc_mean_sd(grp1m = 13.4, grp1sd = 11.6, grp1n = 14, grp2m = 17.4, grp2sd = 11.8,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Telch et al. (2001): Beck Depression Inventory 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
depression6 <- esc_mean_sd(grp1m = 9.9, grp1sd = 10, grp1n = 18, grp2m = 12.8, grp2sd = 8.3,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Harley et al. (2008): Hamilton Rating Scale for Depression
depression7 <- esc_mean_sd(grp1m = 11.30, grp1sd = 5.31, grp1n = 10, grp2m = 17.11, grp2sd = 6.3,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Harley et al. (2008): Beck Depression Inventory
depression8 <- esc_mean_sd(grp1m = 15.10, grp1sd = 12.13, grp1n = 10, grp2m = 25.89, grp2sd = 16.30,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Feldman et al. (2009): Hamilton Rating Scale for Depression 
depression9 <- esc_mean_sd(grp1m = 11.30, grp1sd = 5.31, grp1n = 10, grp2m = 17.11, grp2sd = 6.23,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Safer & Joyce (2011): Beck Depression Inventory  
depression10 <- esc_mean_sd(grp1m = 7, grp1sd = 6, grp1n = 41, grp2m = 12, grp2sd = 8.8,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

depressionez <- combine_esc(depression1, depression2, depression3, depression4, depression5, depression6, depression7, depression8, depression9, depression10)

metafor::rma(yi = es, sei = se, method = "REML", data = depressionez)

#  d =  -0.4017 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8

```


# Effect size of Eating  
```{r}

# Safer et al. (2010): Eating Disorder Examination-Restraint
eating1 <- esc_mean_sd(grp1m = 1.29, grp1sd = 1.04, grp1n = 43, grp2m = 1.91, grp2sd = 1.23,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Eating Disorder Examination-Weight Concerns 
eating2 <- esc_mean_sd(grp1m = 2.54, grp1sd = 1.18, grp1n = 43, grp2m = 3, grp2sd = 1.25,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Eating Disorder Examination-Shape Concerns
eating3 <- esc_mean_sd(grp1m = 2.62, grp1sd = 1.15, grp1n = 43, grp2m = 3.03, grp2sd = 1.35,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Eating Disorder Examination-Eating Concerns
eating4 <- esc_mean_sd(grp1m = 0.54, grp1sd = 0.71, grp1n = 43, grp2m = 1.14, grp2sd = 1.39,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Weight (pounds)
eating5 <- esc_mean_sd(grp1m = 212.61, grp1sd = 52.60, grp1n = 43, grp2m = 221.87, grp2sd = 53.19,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Body Mass Index
eating6 <- esc_mean_sd(grp1m = 35.13, grp1sd = 9.03, grp1n = 43, grp2m = 36.65, grp2sd = 7.64,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2001): Emotional Eating Scale subscore scores - Anger
eating7 <- esc_mean_sd(grp1m = 1.8, grp1sd = 0.8, grp1n = 14, grp2m = 2.6, grp2sd = 0.9,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Safer et al. (2001): Emotional Eating Scale subscore scores - Anxiety
eating8 <- esc_mean_sd(grp1m = 1.3, grp1sd = 0.9, grp1n = 14, grp2m = 2, grp2sd = 0.8,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Safer et al. (2001): Emotional Eating Scale subscore scores - Depression
eating9 <- esc_mean_sd(grp1m = 2.1, grp1sd = 1, grp1n = 14, grp2m = 2.6, grp2sd = 0.7,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Telch et al. (2001): Binge days
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating10 <- esc_mean_sd(grp1m = 0, grp1sd = 0, grp1n = 18, grp2m = 8.5, grp2sd = 10,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Purge days
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating11 <- esc_mean_sd(grp1m = 0, grp1sd = 0, grp1n = 18, grp2m = 10, grp2sd = 14,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Weight (pounds)
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating12 <- esc_mean_sd(grp1m = 209.2, grp1sd = 49, grp1n = 18, grp2m = 223.8, grp2sd = 37.8,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Eating Disorder Examination-Weight Concerns 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating13 <- esc_mean_sd(grp1m = 2.2, grp1sd = 0.9, grp1n = 18, grp2m = 3.1, grp2sd = 1,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Eating Disorder Examination-Shape Concerns 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating14 <- esc_mean_sd(grp1m = 2.3, grp1sd = 0.9, grp1n = 18, grp2m = 3.1, grp2sd = 1,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Eating Disorder Examination-Eating Concerns 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating15 <- esc_mean_sd(grp1m = 0.4, grp1sd = 0.4, grp1n = 18, grp2m = 1.4, grp2sd = 0.9,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Eating Disorder Examination-Restraint
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating16 <- esc_mean_sd(grp1m = 1.4, grp1sd = 1, grp1n = 18, grp2m = 1.8, grp2sd = 1.3,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Binge Eating Scale
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating17 <- esc_mean_sd(grp1m = 15.7, grp1sd = 9.4, grp1n = 18, grp2m = 28.2, grp2sd = 8.3,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Emotional Eating Scale subscore scores - Anger
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating18 <- esc_mean_sd(grp1m = 1.8, grp1sd = 1, grp1n = 18, grp2m = 2.6, grp2sd = 0.9,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Emotional Eating Scale subscore scores - Anxiety
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating19 <- esc_mean_sd(grp1m = 1.5, grp1sd = 0.9, grp1n = 18, grp2m = 2.4, grp2sd = 1,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Emotional Eating Scale subscore scores - Depression
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
eating20 <- esc_mean_sd(grp1m = 2.4, grp1sd = 1, grp1n = 18, grp2m = 3, grp2sd = 0.8,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Safer & Joyce (2011): Objective binge days 
eating20 <- esc_mean_sd(grp1m = 1.7, grp1sd = 4.5, grp1n = 41, grp2m = 4.4, grp2sd = 5.3,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Eating Disorder Examination-Restraint
eating21 <- esc_mean_sd(grp1m = 1.4, grp1sd = 0.94, grp1n = 41, grp2m = 1.8, grp2sd = 1.3,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Eating Disorder Examination-Weight Concerns 
eating22 <- esc_mean_sd(grp1m = 2.5, grp1sd = 1, grp1n = 41, grp2m = 3, grp2sd = 1.3,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Eating Disorder Examination-Shape Concerns 
eating23 <- esc_mean_sd(grp1m = 2.3, grp1sd = 1.1, grp1n = 41, grp2m = 3.2, grp2sd = 1.3,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Eating Disorder Examination-Eating Concerns 
eating24 <- esc_mean_sd(grp1m = 0.4, grp1sd = 0.6, grp1n = 41, grp2m = 1.1, grp2sd = 1.3,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Three Factor Eating Questionnaire-Cognitive Restraint 
eating25 <- esc_mean_sd(grp1m = 10.9, grp1sd = 4, grp1n = 41, grp2m = 9.9, grp2sd = 3.8,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Three Factor Eating Questionnaire-Disinhibition
eating26 <- esc_mean_sd(grp1m = 9.7, grp1sd = 3.8, grp1n = 41, grp2m = 12.2, grp2sd = 3.1,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Three Factor Eating Questionnaire-Hunger
eating27 <- esc_mean_sd(grp1m = 6, grp1sd = 3.9, grp1n = 41, grp2m = 8.4, grp2sd = 3.8,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Body mass index
eating28 <- esc_mean_sd(grp1m = 35.6, grp1sd = 8.3, grp1n = 41, grp2m = 36.1, grp2sd = 8.4,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

# Safer & Joyce (2011): Weight
eating29 <- esc_mean_sd(grp1m = 214.6, grp1sd = 50.4, grp1n = 41, grp2m = 219.1, grp2sd = 54.8,
                  grp2n = 60, es.type = "d", study = "Safer & Joyce 2011")

eatingez <- combine_esc(eating1, eating2, eating3, eating4, eating5, eating6, eating7, eating8, eating9, eating10, eating11, eating12, eating13, eating14, eating15, eating16, eating17, eating18, eating19, eating20, eating21, eating22, eating23, eating24, eating25, eating26, eating27, eating28, eating29)

metafor::rma(yi = es, sei = se, method = "REML", data = eatingez)

#  d =  -0.5377 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8
```

#### Below is work in progress ###############

# Effect size of Psychiatric Symptoms
```{r}
# Soler et al. (2009):  Derogatis Symptom Checklist (SCL90-R) - global severity index
# Assumed N1, N2
psychiatric1 <- esc_mean_sd(grp1m = 2.09, grp1sd = 1.07, grp1n = 23, grp2m = 2.50, grp2sd = 0.86,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Derogatis Symptom Checklist (SCL90-R) - interpersonal sensitivity
# Assumed N1, N2
psychiatric2 <- esc_mean_sd(grp1m = 18.50, grp1sd = 10.05, grp1n = 23, grp2m = 26.00, grp2sd =                      8.34, grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Derogatis Symptom Checklist (SCL90-R) - hostility
# Assumed N1, N2
psychiatric3 <- esc_mean_sd(grp1m = 13.00, grp1sd = 8.59, grp1n = 23, grp2m = 15.85, grp2sd =                       8.17, grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Derogatis Symptom Checklist (SCL90-R) - psychoticism
# Assumed N1, N2
psychiatric4 <- esc_mean_sd(grp1m = 16.37, grp1sd = 11.09, grp1n = 23, grp2m = 22.28, grp2sd =                      9.19, grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Safer et al. (2001): Multidimensional Personality Scale score
pyschiatric5 <- esc_mean_sd(grp1m = 16.4, grp1sd = 5.9, grp1n = 14, grp2m = 15.6, grp2sd = 6.8,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Soler et al. (2009): Brief Psychiatric Rating Scale for psychotic symptoms
# Assumed N1, N2
pyschiatric6 <- esc_mean_sd(grp1m = 8.74, grp1sd = 5.06, grp1n = 23, grp2m = 11.89, grp2sd = 4.40,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")



psychiatric <- combine_esc(psychiatric1, psychiatric2, psychiatric3, psychiatric4)

metafor::rma(yi = es, sei = se, method = "REML", data = psychiatric)

#  d =-0.5371 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8
```





# Effect size of Emotion Processing 
```{r}

# Feldman et al. (2009): Emotional Processing 
emotionalprocessing1 <- esc_mean_sd(grp1m = 3.10, grp1sd = 0.83, grp1n = 10, grp2m = 2.17, grp2sd = .64,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")


```

# Effect size of Self-Esteem  
```{r}

# Safer et al. (2010): Rosenberg Self-Esteem Scale
selfesteem1 <- esc_mean_sd(grp1m = 30.29, grp1sd = 6.89, grp1n = 43, grp2m = 29.82, grp2sd = 5.80,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2001): Rosenberg Self-Esteem Scale
selfesteem2 <- esc_mean_sd(grp1m = 26.4, grp1sd = 5, grp1n = 14, grp2m = 25.4, grp2sd = 6.4,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Telch et al. (2001): Rosenberg Self-Esteem Scale
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
selfesteem3 <- esc_mean_sd(grp1m = 29.4, grp1sd = 6.1, grp1n = 18, grp2m = 29.2, grp2sd = 4.5,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

```

# Effect size of Mood / Affect 
```{r}

# Hirvikoski et al. (2011): Perceived Stress Scale
stress1 <- esc_mean_sd(grp1m = 25.23, grp1sd = 9.39, grp1n = 26, grp2m = 26, grp2sd = 7.74,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")

# Safer et al. (2010): Negative Mood Regulation Scale 
stress2 <- esc_mean_sd(grp1m = 1.83, grp1sd = 0.98, grp1n = 43, grp2m = 2.06, grp2sd = 1.05,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Disorders of Emotion Regulation Scale
stress3 <- esc_mean_sd(grp1m = 75.58, grp1sd = 23.91, grp1n = 43, grp2m = 75.94, grp2sd = 21.04,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Positive and Negative Affect Scale-Positive - positive affect 
stress4 <- esc_mean_sd(grp1m = 30.24, grp1sd = 10.34, grp1n = 43, grp2m = 30.41, grp2sd = 6.97,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2010): Positive and Negative Affect Scale-Positive - negative affect 
stress4 <- esc_mean_sd(grp1m = 21.26, grp1sd = 8.01, grp1n = 43, grp2m = 20.45, grp2sd = 6.58,
                  grp2n = 43, es.type = "d", study = "Safer et al 2010")

# Safer et al. (2001): Negative Mood Regulation Scale score 
stress5 <- esc_mean_sd(grp1m = 96.1, grp1sd = 24, grp1n = 14, grp2m = 97.7, grp2sd = 15,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Safer et al. (2001): Positive and Negative Affect Scale-Positive - positive affect
stress6 <- esc_mean_sd(grp1m = 27.6, grp1sd = 8.2, grp1n = 14, grp2m = 28.3, grp2sd = 7.9,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Safer et al. (2001): Positive and Negative Affect Scale-Positive - negative affect
stress7 <- esc_mean_sd(grp1m = 23.4, grp1sd = 8.4, grp1n = 14, grp2m = 30.0, grp2sd = 9.7,
                  grp2n = 15, es.type = "d", study = "Safer et al 2001")

# Telch et al. (2001): Negative Mood Regulation Scale score 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
stress8 <- esc_mean_sd(grp1m = 110.1, grp1sd = 16.8, grp1n = 18, grp2m = 104.1, grp2sd = 17,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Positive and Negative Affect Scale-Positive - positive affect 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
stress9 <- esc_mean_sd(grp1m = 30, grp1sd = 10.8, grp1n = 18, grp2m = 31.2, grp2sd = 7.8,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")

# Telch et al. (2001): Positive and Negative Affect Scale-Positive - negative affect 
# Assumed N1 (22 - 4 = 18), N2 (22 - 6 = 16)
stress10 <- esc_mean_sd(grp1m = 17.9, grp1sd = 6.7, grp1n = 18, grp2m = 20.6, grp2sd = 8.7,
                  grp2n = 16, es.type = "d", study = "Telch et al 2001")



```

# Effect size of Sleep 
```{r}

# Hirvikoski et al. (2011): Karolinska Sleep Questionnaire - sleep 
sleep1 <- esc_mean_sd(grp1m = 31.88, grp1sd = 15.24, grp1n = 26, grp2m = 28.88, grp2sd = 14.23,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")


```

# Effect size of Suicidiality  
```{r}




```

# Effect size of Disability  
```{r}

# Hirvikoski et al. (2011): Sheehan Disability Scale - disability 
disability1 <- esc_mean_sd(grp1m = 6.23, grp1sd = 1.99, grp1n = 26, grp2m = 6, grp2sd = 2.40,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")


```

# Effect size of Social Adjustment  
```{r}

# Harley et al. (2008): Social Adjustment Scale Self-Report Work Subscale
socialadjustment1 <- esc_mean_sd(grp1m = 65.70, grp1sd = 19.27, grp1n = 10, grp2m = 69.56, grp2sd = 17.66,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Harley et al. (2008): Social Adjustment Scale Self-Report Social or Leisure Subscale
socialadjustment2 <- esc_mean_sd(grp1m = 64.30, grp1sd = 12.91, grp1n = 10, grp2m = 72.56, grp2sd = 16.21,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Harley et al. (2008): Schwartz Outcome Scale 10 - measure satisfaction of mental health outcomes
socialadjustment3 <- esc_mean_sd(grp1m = 35.30, grp1sd = 13.12, grp1n = 10, grp2m = 21.56, grp2sd = 11.09,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")






```

# Effect size of Impaired Functioning 
```{r}

# Harley et al. (2008): Range of Impaired Functioning Tool Work Score
impairedfunctioning1 <- esc_mean_sd(grp1m = 2.70, grp1sd = 1.34, grp1n = 10, grp2m = 3.11, grp2sd = 1.69,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Harley et al. (2008): Range of Impaired Functioning Tool Recreation Score
impairedfunctioning2 <- esc_mean_sd(grp1m = 2.70, grp1sd = 1.06, grp1n = 10, grp2m = 3, grp2sd = 1.19,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")

# Harley et al. (2008): Range of Impaired Functioning Tool Satisfaction Score
impairedfunctioning3 <- esc_mean_sd(grp1m = 2.70, grp1sd = 0.95, grp1n = 10, grp2m = 3.33, grp2sd = 1.19,
                  grp2n = 9, es.type = "d", study = "Harley et al 2008")




```

# Effect size of Borderline Personality Disorder Core Symptoms
```{r}
# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - global
# Assumed N1, N2
bpd1 <- esc_mean_sd(grp1m = 3.50, grp1sd = 1.20, grp1n = 23, grp2m = 4.44, grp2sd = 0.52,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - unstable relations
# Assumed N1, N2
bpd2 <- esc_mean_sd(grp1m = 4.22, grp1sd = 0.80, grp1n = 23, grp2m = 4.44, grp2sd = 0.72,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - impulsivity
# Assumed N1, N2
bpd3 <- esc_mean_sd(grp1m = 3.61, grp1sd = 0.97, grp1n = 23, grp2m = 4.11, grp2sd = 0.60,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - suicide
# Assumed N1, N2
bpd4 <- esc_mean_sd(grp1m = 2.44, grp1sd = 1.24, grp1n = 23, grp2m = 2.55, grp2sd = 0.88,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - affect instability
# Assumed N1, N2
bpd5 <- esc_mean_sd(grp1m = 3.61, grp1sd = 1.19, grp1n = 23, grp2m = 4.66, grp2sd = 0.70,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")


# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - anger
# Assumed N1, N2
bpd6 <- esc_mean_sd(grp1m = 3.11, grp1sd = 1.02, grp1n = 23, grp2m = 3.88, grp2sd = 0.78,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - emptiness
# Assumed N1, N2
bpd7 <- esc_mean_sd(grp1m = 4.33, grp1sd = 1.57, grp1n = 23, grp2m = 5, grp2sd = 1.50,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Clinical Global Impression-Borderline Personality Disorder - Global Improv Patient
# Assumed N1, N2
bpd8 <- esc_mean_sd(grp1m = 3.27, grp1sd = 0.90, grp1n = 23, grp2m = 3.57, grp2sd = 1.13,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

bpd <- combine_esc(bpd1, bpd2, bpd3, bpd4, bpd5, bpd6, bpd7)

metafor::rma(yi = es, sei = se, method = "REML", data = bpd)

#  d =  -0.6244 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8
``` 

# Effect size of Hostility (Irritability)
```{r}
# Soler et al. (2009):  Buss–Durkee Inventory - irritability
# Assumed N1, N2
h1 <- esc_mean_sd(grp1m = 8.38, grp1sd = 3.34, grp1n = 23, grp2m = 9.86, grp2sd = 0.90,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

# Soler et al. (2009):  Buss–Durkee Inventory - indirect hostility
# Assumed N1, N2
h2 <- esc_mean_sd(grp1m = 6.75, grp1sd = 1.88, grp1n = 23, grp2m = 7.57, grp2sd = 1.27,
                  grp2n = 26, es.type = "d", study = "Soler et al 2009")

hostility <- combine_esc(h1, h2)

metafor::rma(yi = es, sei = se, method = "REML", data = hostility)

#  d =  -0.5695 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8
```

# Effect size of Coping
```{r}

# Shelton et al. (2009): Ways of Coping Checklist - planful problem solving 
c1 <- esc_f(f = 5.2, grp1n = 63, grp2n = 61, study = "Shelton et al 2010")

# Shelton et al. (2009): Ways of Coping Checklist - escape-avoidance
c2 <- esc_f(f = 4.51, grp1n = 63, grp2n = 61, study = "Shelton et al 2010")



coping <- combine_esc(c1, c2)

metafor::rma(yi = es, sei = se, method = "REML", data = coping)

#  d = 0.3955 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8
```

# Effect size of Intelligence 
```{r}

# Hirvikoski et al. (2011): Full Scale IQ - intelligence 
s1 <- esc_mean_sd(grp1m = 99.92, grp1sd = 12.58, grp1n = 26, grp2m = 99.87, grp2sd = 12.85,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")


```

# Effect size of ADHD 
```{r}

# Hirvikoski et al. (2011): Wender Utah Rating Scale - childhood ADHD 
adhd1 <- esc_mean_sd(grp1m = 31.88, grp1sd = 15.24, grp1n = 26, grp2m = 28.88, grp2sd = 14.23,
                  grp2n = 25, es.type = "d", study = "Hirvikoski et al 2011")



```

# Effect size of Disciplinary Tickets
```{r}
# Shelton et al. (2009): disciplinary tickets
dt1 <- esc_t(t = 2.292, grp1n = 63, grp2n = 61, study = "Shelton et al 2010")

disctickets <- combine_esc(dt1)
 
metafor::rma(yi = es, sei = se, method = "REML", data = disctickets)

#  d = 0.4117 (medium) 

# Small effect = 0.2, Medium Effect = 0.5, Large Effect = 0.8

```


# Combine all Two Group Effect Sizes into CSV spreadsheet on Excel
```{r}

# This method is a small wrapper to write csv-files. It writes the results from combine_esc into an Excel csv-file.
write_esc(a1, a2, a3, d1, psychiatric1, psychiatric2, psychiatric3, psychiatric4, psychotic1, bpd1, bpd2, bpd3, bpd4, bpd5, bpd6, bpd7, h1, h2, c1, c2, dt1,  path = "EffSizes2Group")

```




###### One group Pre and Post (No Control) ####################################

# Effect size of coping 
```{r}
# Results: To test the hypothesis that participants will show reduced aggression, impulsivity, and improved coping, after completing the DBT-CM groups: physical aggression as measured by BPAQ (t= 7.576, df=21, p=.000) and using distancing (WCCL subscale) as a coping strategy (t=2.529, df=9, p=.032) showed statistical differences at post-test. There was a significant change in disciplinary tickets from pre to posttest (t=2.753, df =24, p =.011), indicating that correctional officers observed an improvement in aggressive and impulsive behavior following the intervention.


# Shelton et al. (2011): WCCL - coping strategy
# N = 26, df = 9, p = .032
esc_t(t = 2.529, grp1n = , grp2n = ) #???paired t-test for one group, no control, pre-post measures

```




# Effect size of Physical Aggression 
```{r}
# Results: To test the hypothesis that participants will show reduced aggression, impulsivity, and improved coping, after completing the DBT-CM groups: physical aggression as measured by BPAQ (t= 7.576, df=21, p=.000) and using distancing (WCCL subscale) as a coping strategy (t=2.529, df=9, p=.032) showed statistical differences at post-test. There was a significant change in disciplinary tickets from pre to posttest (t=2.753, df =24, p =.011), indicating that correctional officers observed an improvement in aggressive and impulsive behavior following the intervention.

# Shelton et al. (2011): BPAQ - physical aggression
# N = 26, df = 21, p = .000
esc_t(t = 7.576, grp1n = , grp2n = ) #???paired t-test for one group, no control, pre-post measures



```




# Effect size of Disciplinary Tickets 
```{r}
# Results: To test the hypothesis that participants will show reduced aggression, impulsivity, and improved coping, after completing the DBT-CM groups: physical aggression as measured by BPAQ (t= 7.576, df=21, p=.000) and using distancing (WCCL subscale) as a coping strategy (t=2.529, df=9, p=.032) showed statistical differences at post-test. There was a significant change in disciplinary tickets from pre to posttest (t=2.753, df =24, p =.011), indicating that correctional officers observed an improvement in aggressive and impulsive behavior following the intervention.

# Shelton et al. (2011): disciplinary tickets
# N = 26, df = 24, p = .011
esc_t(t = 2.753, grp1n = , grp2n = ) #???paired t-test for one group, no control, pre-post measures

```











# 